%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{itemize}

	\item
	{\textbf{Bus Traking System:} It's an application to trace buses with help of GPS system of android phone. I use spring framework technology for server side and client side application, android application to get GPS location. Source code for server side application \underline{https://github.com/touhidhossain/BusTracking} \& Source code for geting GPS location \underline{https://github.com/touhidhossain/BusTracker} }
	
	\item
	{\textbf{Electric Music Shop:} You can buy musical from this site. Java, Spring MVC, Angularjs, PostgreSQL, GIT are used to develop this application. Source code \underline{https://github.com/touhidhossain/musicStore} }
	
	\item
	{\textbf{Food Order Management System of Restaurant:} Customer could order food with help of this application. Java servlet, PostgreSQL are used to develop this application}
	
	\item
	{\textbf{Electric Banking and Payment System:} Balance transfer, Request for fund, Balance check, Pay for Online shopping is main feature of this application. Java, Spring MVC, PostgreSQL are used to develop this application}
	
	\item
	{\textbf{Remotely PC Control:} It's a application like teamviewer. You could remotely access your friend’s pc and could do typing, mouse control etc.}
	
\end{itemize}